---
title: "Life Satisfaction vs Life Expectancy"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
```

## Introductory Paragraph
The purpose of our project is to demonstrate how, as life expectancy increases,
life satisfaction tends to increase as well.

Our dataset consists of values listing **life satisfaction** and **life expectancies** of various countries over a period of time. Levels of life satisfaction are measured based on the Cantril Ladder. We retrieved the dataset from 9 different data sources:

* [World Happiness Report](https://worldhappiness.report/)
* [European Commission – Eurobarometer Interactive](http://ec.europa.eu/commfrontoffice/publicopinion/index.cfm/Chart/index)
* [The World Value Survey (WVS)](http://www.worldvaluessurvey.org/WVSDocumentationWVL.jsp)
* [Pew Global Attitudes Survey](www.pewglobal.org)
* [US General Social Survey](https://gssdataexplorer.norc.org)
* [British Office for National Statistics](https://gssdataexplorer.norc.org)
* [Germany – Deutsche Post Glücksatlas](http://www.gluecksatlas.de/)


```{r echo = FALSE, warning=FALSE}
source("calc_sum.R")
df <- read.csv("data/life-satisfaction-vs-life-expectancy.csv",
  stringsAsFactors = FALSE
)
df_filter <- df %>%
  filter(
    !is.na
    (Life.satisfaction..measured.from.lowest.0.to.highest.10.on.Cantril.Ladder.)
  ) %>%
  filter(!is.na(Life.expectancy..years.)) %>%
  select(-Total.population..Gapminder.)

list <- get_summary_info(df_filter)
```
## Summary Paragraph
We created a summary to calculate various helpful observations: 

* Number of entries = `r list$rows`
* Average life expectancy = `r list$life_exp_mean`
* Average life satisfaction = `r list$life_sat_mean`
* Minimum life expectancy = `r list$life_exp_min`
* Minimum life satisfaction = `r list$life_sat_min`
* Maximum life expectancy = `r list$life_exp_max`
* Maximum life satisfaction = `r list$life_sat_max`

## Aggregate Table
```{r include=FALSE, warning=FALSE}
source("return_sum_info.R")
```
`r kable(avg, col.names=c("Entity", "Average Life Expectancy", "Average Life Satisfaction"))`

* The country with the _highest_ average life expectancy is
`r avg %>% filter(avg_life_exp == max(avg_life_exp)) %>% pull(Entity)`
(`r avg %>% filter(avg_life_exp == max(avg_life_exp)) %>% pull(avg_life_exp)`
years).
* The country with the _lowest_ average life expectancy is
`r avg %>% filter(avg_life_exp == min(avg_life_exp)) %>% pull(Entity)`
(`r avg %>% filter(avg_life_exp == min(avg_life_exp)) %>% pull(avg_life_exp)`
years).
* The country with the _highest_ average life satisfaction is
`r avg %>% filter(avg_life_satisf == max(avg_life_satisf)) %>% pull(Entity)`
(`r avg %>% filter(avg_life_satisf == max(avg_life_satisf)) %>% pull(avg_life_satisf)`
years).
* The country with the _lowest_ average life satisfaction is
`r avg %>% filter(avg_life_satisf == min(avg_life_satisf)) %>% pull(Entity)`
(`r avg %>% filter(avg_life_satisf == min(avg_life_satisf)) %>% pull(avg_life_satisf)`
years).

We grouped the data by using the _mean_ aggregate function because this
provides a good representation of each country's statistics. It is more useful
to show their averages rather than data from a particular year because this
minimizes outliers.


## Table Observations

### Chart 1
```{r echo=FALSE, warning=FALSE}
source("chart1.R")
chart1(df)
```
The purpose of chart 1 is to detail how as life satisfaction increases,
the range of life expectancy tends to cluster towards a higher life
expectancy. As you can see, the general trend is: as life satisfaction goes up,
life expectancy does as well. Ultimately, life satisfaction and life
expectancy are correlated, but one does not necessarily cause the other.

### Chart 2
```{r include=FALSE, warning=FALSE}
source("chart2.R")
```
`r chart2(df)`

This chart compares the average life expectancy and average life satisfaction
for each country. Each country is displayed as a different data point, in
varying colors. There is a positive general trend: as life expectancy
increases, life satisfaction also goes up.

### Chart 3
```{r include=FALSE,warning=FALSE}
source("chart3.R")
```
`r life_exp_overtime(df)`

This graphs depicts how life expectancy has increased throughout the 20th and
21st centuries. There is a steady increase in life expectancy. Each data point
is the life expectancy of all the countries combined. Although there are some
countries that have higher life expectancies, the overall population of the
world still experiences an increase in their life spans.
