---
title: "Life Satisfaction vs Life Expectancy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Introductory Paragraph
Our dataset consists of values listing **life satisfaction** and **life expectancies** of various countries over a period of time. Levels of life satisfaction are measured based on the Cantril Ladder. We retrieved the dataset from 9 different data sources:

* [World Happiness Report](https://worldhappiness.report/)
* [European Commission – Eurobarometer Interactive](http://ec.europa.eu/commfrontoffice/publicopinion/index.cfm/Chart/index)
* [The World Value Survey (WVS)](http://www.worldvaluessurvey.org/WVSDocumentationWVL.jsp)
* [Pew Global Attitudes Survey](www.pewglobal.org)
* [US General Social Survey](https://gssdataexplorer.norc.org)
* [British Office for National Statistics](https://gssdataexplorer.norc.org)
* [Germany – Deutsche Post Glücksatlas](http://www.gluecksatlas.de/)


```{r echo = FALSE}
source("calc_sum.R")
df <- read.csv("data/life-satisfaction-vs-life-expectancy.csv",
               stringsAsFactors = FALSE)
df_filter <- df %>%
filter(
!is.na
  (Life.satisfaction..measured.from.lowest.0.to.highest.10.on.Cantril.Ladder.)
) %>%
  filter(!is.na(Life.expectancy..years.)) %>%
  select(-Total.population..Gapminder.)

list <- get_summary_info(df_filter)
```
## Summary Paragraph
We created a summary to calculate: 

* Number of entries = `r list$rows`
* Average life expectancy = `r list$life_exp_mean`
* Average life satisfaction = `r list$life_sat_mean`
* Minimum life expectancy = `r list$life_exp_min`
* Minimum life satisfaction = `r list$life_sat_min`
* Maximum life expectancy = `r list$life_exp_max`
* Maximum life satisfaction = `r list$life_sat_max`



Render your table and describe pertinent observations found in it
## Table Observations

Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart
## Chart 1
## Chart 2
## Chart 3
